A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-29 4_method.tex
revamp distance_based_angles and distance_ratio_limit figures

\begin{figure}
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{
Distance based angle estimation.
By comparing the Euclidean distance between two vertices with the feature radius $R$ we can skip comparing the angles between the outline segments.
}
\label{distance_based_angles}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
\caption{Minimal Euclidean distance for a given difference in feature radius $R$.}
\label{distance_ratio_limit}
\end{figure}

>>>>

\begin{figure} \centering
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=.7\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{Significance}
\label{distance_based_angles}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=.7\columnwidth]{sources/method/distance_ratio_limit.pdf}
\caption{Distance}
\label{distance_ratio_limit}
\end{subfigure}
\caption{
Properties of feature radius $R$.
Part of outline shape in thick black,
skeleton in red,
inscribed circle in gray,
radii in dashed lines.
The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
}
\end{figure}

@@
